Honors Thesis Proposal

### 2010-10-02 honors_thesis/si_paper/paper.tex
I made some revisions to the SI paper according to feedback from TEC

Particle swarm optimization (PSO) has previously been parallelized primarily by
distributing the computation corresponding to particles across multiple
processors.  In these approaches, additional processors can only add more
particles to the swarm.  However, in many cases this is not efficient when
scaled to very large swarm sizes (on very large clusters).  In this paper we
present a different way of using additional processors in the computation of
PSO motivated by speculative execution in modern computer hardware.  We call
our method Speculative Evaluation in PSO (SEPSO).

In SEPSO future positions of the particles are speculated and evaluated in
parallel with the evaluation of current positions.  We show that a set of
speculative evaluations can be constructed such that the set will always
include the position and corresponding evaluation that would normally have
occurred at the next iteration of standard PSO.  Thus SEPSO performs two
iterations of PSO at once, allowing it to achieve better fitness faster.

Speculative Evaluation in PSO can be enhanced by diverging from the behavior of
the standard PSO.  We present several variations on our speculative algorithm,
such as making use of the information obtained by the extra speculative
evaluations, and speculating more than one iteration ahead.  Using these
algorithmic modifications, we see dramatic improvements in the effectiveness of
the algorithm.

@@

These previous parallel techniques distribute the computation needed by the
particles in the swarm over the available processors.  If more processors are
available, these techniques increase the number of particles in the swarm,
either by adding individual particles or by adding entire new sub-swarms.  In
almost all cases, adding additional particles produces better results in the
same amount of time.  In \fig{iters-sphere} we see an example of this on the
well-known benchmark function Sphere (20 dimensions, reporting the average of
twenty runs).  In terms of the number of iterations performed (which is
equivalent to wall-clock time if all particles are evaluated in parallel),
every time the swarm size increases, the performance improves.

@@

To solve this problem, we propose a method for performing two iterations of PSO
at the same time in parallel that we call speculative evaluation.  The name
comes from an analogy to speculative execution (also known as branch
prediction), a technique commonly used in processors.  Modern processors, when
faced with a branch on which they must wait (e.g., a memory cache miss), guess
which way the branch will go and start executing, ensuring that any changes can
be undone.  If the processor guesses right, execution is much farther ahead
than if it had idly waited on the memory reference.  If it guesses wrong,
execution restarts where it would have been anyway.

@@

Furthermore, we show that if we relax the requirements of the algorithm, no
longer demanding that it strictly reproduce the exact behavior of standard PSO,
we can introduce new speculative techniques that often out-perform PSO.  These
variants make better use of the information obtained from the extra exploration
made by the speculative function evaluations.  We also explore the idea that,
like branch prediction in processors, we need not speculatively evaluate
\emph{all} possible future positions, we can accelerate the algorithm even if
we are just \emph{likely} to have guessed right.  By pruning the speculation to
just paths that are statistically likely to reproduce the paths that are
equivalent to PSO we can increase the swarm size without increasing the number
of speculative evaluations.  We also consider several recovery strategies for
cases where the pruned set of speculative evaluations does not contain the
evaluation that standard PSO would have done.  A further improvement we explore
is speculating several iterations ahead instead of just one, which is made
possible by pruning the number of speculative evaluations.

@@

PSO can be trivially parallelized by assigning each particle's computation to
an individual processor.  But as we have seen in \fig{evals-sphere}, for some
functions, and for large numbers of processors, just adding particles reaches a
point of diminishing returns.  That is, adding processors does not help the
algorithm reach any given level of fitness appreciably faster.  Instead of
adding particles we employ a speculative approach that allows us to perform
iterations two at a time.

@@

The refactoring hinges on the idea that once the random coefficients
$\pURand_{t}$ and $\pURand_{t}$ are determined, there are only a few possible
updates to $\nbest$ and $\pbest$.  For the Ring topology there are 7 possible
update cases, identified in Table~\ref{tab:evals}.  We label each case with an
identifier referring to the source of the update: a minus sign ($-$) represents
no update, $L$ represents an update to $\nbest$ coming from the left neighbor,
$R$ represents an update to $\nbest$ coming from the right neighbor, and $S$
represents an update to either $\pbest$ or $\nbest$ coming from the particle
itself.  As an example, $\casexn$ refers to the case that the particle finds a
new personal best, but neither it nor its neighbors find a position that
updated its neighborhood best.  In the equations that follow, we refer to an
unspecified update case as $\casegen$, and to the set of cases collectively as
$\caseset$.

@@

To aid in describing our methodology, we introduce a few terms.  A particle's
set of \emph{speculative children} is the set of all possible next iteration
states that a particle could have.  We use $\p_t$ to denote a particle at
iteration $t$ and $\s_{t+1}$ to denote one of $\p_t$'s speculative children,
corresponding to one of the rows in Table~\ref{tab:evals}.  $\n_t$ is a
neighbor of particle $\p_t$.  Sets of particles are given by $\pset$, $\sset$,
or $\nset$, whereas single particles are simply $\p$, $\s$, or $\n$.

@@

Given a set of particles at iteration $t-1$ (perhaps which have just been
initialized), the master must move each particle using \eqref{eq:velupdate} and
\eqref{eq:posupdate} to obtain the set $\noeval{\pset}_t$.  For each particle
$\noeval{\p}_t$, the master must then get its set of neighbors
$\noeval{\nset}_t$ and use their positions, along with the position of
$\noeval{\p}_t$, to calculate all possible values of
$\specpos_{t+1}^{\casegen}$, using \eqref{eq:defpcasegen}.  These positions,
along with the original particle's associated information (such as values for
$\pbest$ and $\nbest$), define a set of speculative children,
$\noeval{\sset}_{t+1}$.  The master than has a set of particles
$\noeval{\pset}_t$, and for each particle a set of speculative children
$\noeval{\sset}_{t+1}$, which can all be evaluated at once.

The master then has the slaves evaluate the particles.  Once all particles,
speculative and original, have been evaluated and the values reported to the
master, the master determines which speculative child of each particle was the
correct one.  Mathematically, this corresponds to the evaluation of an
indicator function similar to that found in \eqref{eq:deficasexn}.  In
practice, this is done first by updating each particle's $\pbest$, if
necessary, then by updating the particle's $\nbest$ with information from the
particle's neighbors.  This is simply the original PSO algorithm, and
corresponds to steps 1--5 in \alg{centralized}.  Given the updates to $\pbest$
and $\nbest$, the case from Table~\ref{tab:evals} can be determined, as per
\eqref{eq:val2updatelong}.  The child with the matching case is kept, and all
other speculative children are discarded (step 7 in \alg{centralized}.

The parent $\p_t$ must pass its personal best value to the child, as the child
knows only the position that it guessed, not the function value at that
position.  It is possible that both $\p_t$ and $\s_{t+1}$ update their personal
bests, but $\p_t$'s value is better.  For example, suppose that $\p_{t-1}$ has
a personal best value of 3, and the we are seeking to minimize the function.
$\noeval{\p}_t$ is created, and $\noeval{\s}_{t+1}$ is moved assuming that
$\p_t$ has updated its personal best with its position at time $t$.  Then both
$\noeval{\p}_t$ and $\noeval{\s}_{t+1}$ are evaluated, with values 1 and 2,
respectively.  $\nonbest{\s}_{t+1}$ would think that its current position is
its personal best, as the value it found, 2, is better than its previous
personal best value of 3.  It needs to receive the personal best value from its
parent to know that its personal best position $\pbest$ is actually the
position of $\p_t$, not $\s_{t+1}$.

@@

To perform speculative evaluation in a distributed PSO algorithm, there must be
some way to have processors evaluate the speculative children of particles,
without giving the speculative particles the same treatment as actual
particles, as the speculative children only live for one iteration.  One way
that can be done is by assigning each particle a set of machines instead of a
single machine, and the particle directs its extra machines to evaluate its
speculative children.  However the distributed framework functions, the same
information needs to be passed between particles, and we describe here the
messages each particle needs to receive to perform speculative evaluation.

@@

Performing speculative evaluation in PSO with a dynamic topology raises a
sticky issue of its own.  In a static topology, at iteration $t$ a particle
already has all of the information about the positions of its neighbors during
iterations $1$ through $t-1$.  If the neighbor finds a better position at
iteration $t$, the particle updates its neighborhood best, but if it does not,
it still has its old neighborhood best from its neighbors for all previous
iterations.

@@

A more principled approach would be to use the statistical behavior of PSO to
find probabilities of taking any particular branch.  While we cannot with
certainty predict which branch a particle will take every time, if we can use
statistics to narrow down the $2(n+1)$ possible evaluations to a few likely
candidates, we can decrease the amount of computation required to do
speculative evaluation and improve our performance.

@@

Using the same number of processors for each algorithm requires that our
speculative algorithms have a smaller swarm size than standard PSO.  For each
of the topologies we used, a particle has three neighbors including itself.  As
shown in Table~\ref{tab:evals}, this results in $7$ speculative evaluations per
particle.  With one evaluation needed for the original, non-speculative
particle, we have $8p$ evaluations for every two iterations, where $p$ is the
number of particles in the speculative swarm.  The extra evaluations done in
speculative evaluation would instead be particles in regular PSO, so we compare
swarms of size $p$ in speculative evaluation with swarms of size $8p$ in
regular PSO.

Where the Complete topology would normally be used, we use a Random topology in
our speculative algorithm, as Complete leads to an explosion in the number of
speculative evaluations.  If speculative evaluation were not being performed,
it is possible that the Complete topology would be used.  However, the Complete
topology also requires a very large amount of interprocessor communication in
distributed PSO, so it is still quite possible that Random would be used even
with standard PSO.  But, to be fair in our comparisons, we compare to the
standard PSO algorithm using both the Random topology with two neighbors and
the Complete topology (labeled PSO Random and PSO Complete in our results).

@@

The algorithms we compare are the standard PSO algorithm, SEPSO, and four
variations on SEPSO.  In presenting our results, we call the variant developed
in \sec{pickbest} Pick Best.  The algorithms described in \sec{pruning} through
\sec{wrong} are called Pick Best Pruned and Social Promotion Pruned, and the
algorithm in \sec{manyiters} we call Many Iterations.

When performing pruning in SEPSO in Pick Best Pruned and Social Promotion
Pruned, there are a large number of ways to prune speculative evaluations.  We
experimented with several, but present results for only one possible pruning.
The pruning we present uses only the two most probable branches in the Random
topology.  As seen in Table~\ref{tab:stats}, these are the two branches where
the $\nbest$ value was not updated: \casepn\ and \casexn.  Those branches are
also convenient in that no messages are needed from neighbors in order to
produce the positions of the speculative particles---in distributed frameworks
using several rounds of communication (see \sec{distributed}), one of the
rounds of communication can be dropped entirely.

Because pruning only requires two speculative evaluations per particle (along
with evaluating the original particle), we can use swarms of size $3p$ to
compare to a swarm of size $p$ with standard PSO, instead of $8p$ with other
techniques.

@@

When we introduce pruning, our intuition about Pick Best turns out to be more
correct.  While adding 50 more particles to the swarm, Pick Best with pruning
still gets stuck just as often as the original Pick Best.  However, Social
Promotion does well with pruning; it increases the success rate to close to
100\%, while still finding the optimum on average much faster than the original
PSO.

@@

We have given five different variants of speculative evaluation, each of which
has different properties.  The variants of the algorithm perform differently on
different functions and at different swarm sizes, as would be expected by the
No Free Lunch Theorem~\cite{wolpert-1997-nfl-for-optimization}.  We have given
a brief evaluation of the premature convergence properties of these variants on
deceptive functions.  Though there is no one variant that performs best across
all functions, for all but one of the functions we looked at \emph{some} kind
of speculative evaluation outperforms standard PSO, often dramatically.

@@

@@

\bibliographystyle{unsrt}
\bibliography{%
../../../bib/aml/bib,%
../../../bib/nfl/bib,%
../../../bib/optimization/bib,%
../../../bib/pso/general/bib,%
../../../bib/pso/parallel/bib,%
../../../bib/pso/topology/bib,%
../../../bib/sim-anneal/parallel/bib,%
../../../bib/ga/bib}

>>>>

Particle swarm optimization (PSO) has previously been parallelized primarily by
distributing the computation corresponding to particles across multiple
processors.  In these approaches, additional processors can only add more
particles to the swarm.  However, in many cases this is not efficient when
scaled to very large swarm sizes (on very large clusters).  Current methods
cannot answer well the question, ``What do you do with 1000 processors when 50
or 100 particles is the most efficient swarm size?''  In this paper we attempt
to answer that question with a speculative approach to the parallelization of
PSO motivated by speculative execution in modern computer hardware.

In our approach, we refactor PSO such that the computation needed for iteration
$t+1$ can be done in parallel with the computation needed for iteration $t$.
Thus we can perform two iterations of PSO at once.  Even with some amount of
wasted computation, we show that this approach to parallelization in PSO often
outperforms the na\"ive parallelization of simply adding particles to the
swarm.  Our methods produce results that are exactly equivalent to PSO; this is
not a new algorithm or variant, only a new method of parallelization.

However, given this new parallelization model we can relax the requirement of
exactly reproducing PSO in an attempt to produce better results.  We present
several such relaxations, including keeping the best speculative position
evaluated instead of the one corresponding to PSO, and speculating several
iterations ahead instead of just one.  We show that these methods dramatically
improve the performance of parallel PSO in many cases.

@@

These previous parallel techniques distribute the computation needed by the
particles in the swarm over the available processors.  If more processors are
available, these techniques increase the number of particles in the swarm,
either by adding individual particles or by adding entire new sub-swarms.  In
almost all cases, adding additional particles produces better results in the
same amount of time~\cite{mcnabb-2009-large-particle-swarms}.  In
\fig{iters-sphere} we see an example of this on the well-known benchmark
function Sphere (20 dimensions, reporting the average of twenty runs).  In
terms of the number of iterations performed (which is equivalent to wall-clock
time if all particles are evaluated in parallel), every time the swarm size
increases, the performance improves.

@@

To solve this problem, we apply the concept of speculative
decomposition~\cite{grama-2003-intro-to-parallel-computing} to particle swarm
optimization, using extra processors to perform two iterations of PSO at the
same time.  Speculative decomposition is analogous to speculative execution
(also known as branch prediction), a technique commonly used in processors.
Modern processors, when faced with a branch on which they must wait (e.g., a
memory cache miss), guess which way the branch will go and start executing,
ensuring that any changes can be undone.  If the processor guesses right,
execution is much farther ahead than if it had idly waited on the memory
reference.  If it guesses wrong, execution restarts where it would have been
anyway.

@@

It is important to note here that this is not a variant of PSO.  We are not
proposing a new algorithm, and we do not try to beat the state of the art in
PSO research.  We simply propose a new way to think about the parallelization
of PSO that we show works better in many cases than a na\"ive parallelization.

Furthermore, we show that if we relax the requirements of the algorithm, no
longer demanding that it strictly reproduce the exact behavior of standard PSO,
we can introduce new speculative techniques that often out-perform PSO.  These
relaxations make better use of the information obtained from the extra
exploration made by the speculative function evaluations.  We also explore the
idea that, like branch prediction in processors, we need not speculatively
evaluate \emph{all} possible future positions, we can accelerate the algorithm
even if we are just \emph{likely} to have guessed right.  By pruning the
speculation to just paths that are statistically likely to reproduce the paths
that are equivalent to PSO we can increase the swarm size without increasing
the number of speculative evaluations.  We also consider several recovery
strategies for cases where the pruned set of speculative evaluations does not
contain the evaluation that standard PSO would have done.  A further
improvement we explore is speculating several iterations ahead instead of just
one, which is made possible by pruning the number of speculative evaluations.

@@

PSO can be trivially parallelized by assigning each particle's computation to
an individual processor.  But as we have seen in \fig{evals-sphere}, for some
functions, and for large numbers of processors, just adding particles reaches a
point of diminishing returns.  That is, adding processors does not help the
algorithm reach any given level of fitness appreciably faster.  Instead of
adding particles we employ a speculative approach that allows us to perform
two iterations at a time.

@@

The refactoring hinges on the idea that once the random coefficients
$\pURand_{t}$ and $\nURand_{t}$ are determined, there are only a few possible
new positions, or updates, for $\nbest$ and $\pbest$.  For the Ring topology
there are 7 possible update cases, identified in Table~\ref{tab:evals}.  We
label each case with an identifier referring to the source of the update: a
minus sign ($-$) represents no update, $L$ represents an update to $\nbest$
coming from the left neighbor, $R$ represents an update to $\nbest$ coming from
the right neighbor, and $S$ represents an update to either $\pbest$ or $\nbest$
coming from the particle itself.  As an example, $\casexn$ refers to the case
that the particle finds a new personal best, but neither it nor its neighbors
find a position that updated its neighborhood best.  In the equations that
follow, we refer to an unspecified update case as $\casegen$, and to the set of
cases collectively as $\caseset$.

@@

To aid in describing our methodology, we introduce a few terms.  A particle's
set of \emph{speculative children} is the set of all possible next iteration
states (including the particle's position, $\nbest$ and $\pbest$ positions)
that a particle could have.  We use $\p_t$ to denote a particle at iteration
$t$ and $\s_{t+1}$ to denote one of $\p_t$'s speculative children,
corresponding to one of the rows in Table~\ref{tab:evals}.  $\n_t$ is a
neighbor of particle $\p_t$.  Sets of particles are given by $\pset$, $\sset$,
or $\nset$, whereas single particles are simply $\p$, $\s$, or $\n$.

@@

Given a set of particles at iteration $t-1$ (perhaps which have just been
initialized), the master must move each particle using \eqref{eq:velupdate} and
\eqref{eq:posupdate} to obtain the set $\noeval{\pset}_t$.  For each particle
$\noeval{\p}_t$, the master must then get its set of neighbors
$\noeval{\nset}_t$ and use their positions, along with the position of
$\noeval{\p}_t$, to calculate all possible values of
$\specpos_{t+1}^{\casegen}$, using \eqref{eq:defpcasegen}.  These positions,
along with the original particle's associated information (such as values for
$\pbest$ and $\nbest$), define a set of speculative children,
$\noeval{\sset}_{t+1}$.  The master then has a set of particles
$\noeval{\pset}_t$, and for each particle a set of speculative children
$\noeval{\sset}_{t+1}$, which can all be evaluated at once.

The master then has the slaves evaluate the particles.  Once all particles,
speculative and original, have been evaluated and the values reported to the
master, the master determines which speculative child of each particle was the
correct one.  Mathematically, this corresponds to the evaluation of an
indicator function similar to that found in \eqref{eq:deficasexn}.  In
practice, this is done first by updating each (original) particle's $\pbest$,
if necessary, then by updating the particle's $\nbest$ with information from
the particle's neighbors.  This is simply the original PSO algorithm, and
corresponds to steps 1--5 in \alg{centralized}.  Given the updates to $\pbest$
and $\nbest$, the case from Table~\ref{tab:evals} can be determined, as per
\eqref{eq:val2updatelong}.  The child with the matching case is kept, and all
other speculative children are discarded (step 7 in \alg{centralized}).

The parent $\p_t$ must pass its personal best value to the child, as the child
knows only the position that it guessed, not the function value at that
position.  It is possible that both $\p_t$ and $\s_{t+1}$ update their personal
bests, but $\p_t$'s value is better.  For example, suppose that $\p_{t-1}$ has
a personal best value of 3, and that we are seeking to minimize the function.
$\noeval{\p}_t$ is created, and $\noeval{\s}_{t+1}$ is moved assuming that
$\p_t$ has updated its personal best with its position at time $t$.  Then both
$\noeval{\p}_t$ and $\noeval{\s}_{t+1}$ are evaluated, with values 1 and 2,
respectively.  $\nonbest{\s}_{t+1}$ would think that its current position is
its personal best, as the value it found, 2, is better than its previous
personal best value of 3.  It needs to receive the personal best value from its
parent to know that its personal best position $\pbest$ is actually the
position of $\p_t$, not $\s_{t+1}$.

@@

To perform speculative evaluation in a distributed PSO algorithm, there must be
some way to have processors evaluate the speculative children of particles,
without giving the speculative particles the same treatment as actual
particles, as the speculative children only live for one iteration.  One way
that can be done is by assigning each particle a set of machines instead of a
single machine, and the particle directs its extra machines to evaluate its
speculative children.  The same information needs to be passed between
particles no matter the framework used.  We describe here the messages each
particle needs to receive to perform speculative evaluation.

@@

Performing speculative evaluation in PSO with a dynamic topology (where
neighbors change from iteration to iteration) raises a sticky issue of its own.
In a static topology, at iteration $t$ a particle already has all of the
information about the positions of its neighbors during iterations $1$ through
$t-1$.  If the neighbor finds a better position at iteration $t$, the particle
updates its neighborhood best, but if it does not, it still has its old
neighborhood best from its neighbors for all previous iterations.

@@

A more principled approach would be to use the statistical behavior of PSO to
find probabilities of taking any particular branch.  While we cannot with
certainty predict which branch a particle will take every time, if we can use
statistics to narrow down the $2n+1$ possible evaluations to a few likely
candidates, we can decrease the amount of computation required to do
speculative evaluation and improve our performance.

@@

Using the same number of processors for each algorithm requires that our
speculative algorithms have a smaller swarm size than standard PSO.  For each
of the topologies we used, a particle has three neighbors including itself.  As
shown in Table~\ref{tab:evals}, this results in $7$ speculative evaluations per
particle.  With one evaluation needed for the original, non-speculative
particle, we have $8p$ evaluations for every two iterations, where $p$ is the
number of particles in the speculative swarm.  The extra evaluations required
in our speculative approach would instead be used to evaluate particles in
regular PSO, so we compare swarms of size $p$ in speculative evaluation with
swarms of size $8p$ in regular PSO.

Where the Complete topology would normally be preferred, we use a Random
topology in our speculative algorithm, as Complete leads to an explosion in the
number of speculative evaluations.  If speculative evaluation were not being
performed, it is possible that the Complete topology would be used.  However,
the Complete topology also requires a very large amount of interprocessor
communication in distributed PSO, so it is still quite possible that Random
would be used even with standard PSO.  But, to be fair in our comparisons, we
compare to the standard PSO algorithm using both the Random topology and the
Complete topology (labeled PSO Random and PSO Complete in our results).

@@

The algorithms we compare are the standard PSO algorithm, our original
speculative approach (here labeled SEPSO simply for ease of reference), and the
four relaxations of SEPSO discussed in \sec{relax}.  In presenting our results,
we call the approach developed in \sec{pickbest} Pick Best.  The algorithms
described in \sec{pruning} through \sec{wrong} are called Pick Best Pruned and
Social Promotion Pruned, and the algorithm in \sec{manyiters} we call Many
Iterations.

When performing pruning in Pick Best Pruned and Social Promotion Pruned, there
are a large number of ways to prune speculative evaluations.  We experimented
with several, but present results for only one possible pruning.  The pruning
we present uses only the two branches where the $\nbest$ value was not updated:
\casepn\ and \casexn.  Those branches are convenient in that no messages are
needed from neighbors in order to produce the positions of the speculative
particles---in distributed frameworks using several rounds of communication
(see \sec{distributed}), one of the rounds of communication can be dropped
entirely.

Because pruning only requires two speculative evaluations per particle (along
with evaluating the original particle), we can use swarms of size
$\frac{1}{3}p$ to compare to a swarm of size $p$ with standard PSO, instead of
$\frac{1}{8}p$ with other techniques.

@@

When we introduce pruning, our intuition about Pick Best turns out to be more
correct.  While adding 50 more particles to the swarm (as pruning allows us to
have 80 particles with 240 processors instead of only 30), Pick Best with
pruning still gets stuck just as often as the original Pick Best.  However,
Social Promotion does well with pruning; it increases the success rate to close
to 100\%, while still finding the optimum on average much faster than the
original PSO.  These results are shown in \fig{griewank-pruned}.

@@

What we have presented is not a new algorithm or a variant of PSO, and thus we
did not compare our methods against the state of the art in PSO research.  We
presented a new parallelization technique, so we compared parallelization
strategies on the same algorithm, the original PSO.

We have given five different possible approaches to speculative evaluation,
each of which has different properties.  These approaches perform differently
on different functions and at different swarm sizes, as would be expected by
the No Free Lunch Theorem~\cite{wolpert-1997-nfl-for-optimization}.  We have
given a brief evaluation of the premature convergence properties of these
methods on deceptive functions.  Though there is no one approach that performs
best across all functions, for all but one of the functions we looked at
\emph{some} kind of speculative evaluation outperforms standard PSO, often
dramatically.  Our purpose has been simply to show that in many cases
speculative techniques outperform additional particles as the swarm size gets
large; our results are conclusive in that regard.  We are arguing for the
speculative parallelization of PSO, not for one particular approach to it.

@@

We have presented a new paradigm for parallelizing the particle swarm
optimization algorithm, focusing on PSO itself and not all of its variants.  It
remains as future work to apply speculative approaches to recent and popular
PSO variants, such as the Fully Informed Particle
Swarm~\cite{mendes-2004-fully-informed-particle-swarm}.  While our methods will
not always be immediately applicable to every variant, we are confident that
some kind of speculative approach will be beneficial to the parallelization of
all forms of PSO, especially as the number of processors used gets into the
thousands.

@@

\bibliographystyle{unsrt}
\bibliography{%
../../../bib/aml/bib,%
../../../bib/nfl/bib,%
../../../bib/optimization/bib,%
../../../bib/parallel/bib,%
../../../bib/pso/general/bib,%
../../../bib/pso/parallel/bib,%
../../../bib/pso/fips/bib,%
../../../bib/pso/topology/bib,%
../../../bib/sim-anneal/parallel/bib,%
../../../bib/ga/bib}
